### 2020-06-19 docs/LaTex/Paper.tex
Completes docs and includes a new testing version for dendro.ino

\begin{itemize}
  \item \textit{LoRa GPS HAT for Raspberry Pi,}\cite{DraginoRpiHat} which makes use of the extended 40-pin GPIO header to be plugged\footnote{It is important to note this LoRa HAT is not actually designed to play a gateway role, in fact, this is considered a \enquote{Hack where a node-class radio tries to impersonate a gateway}\cite{RpiHatHack},\doubt{(I'm not sure about this citation (It's a forum))} so this means this hat is designed to be a node-class radio, not a gateway.}
  \item \textit{LoRa Shield for Arduino}\cite{DraginoArdShield}, which is plugged through analog and digital pins.
\end{itemize}

@@

>>>>

\begin{itemize}
  \item \textit{LoRa GPS HAT for Raspberry Pi,}\cite{DraginoRpiHat} which makes use of the extended 40-pin GPIO header to be plugged\footnote{It is important to note this LoRa HAT is not actually designed to play a gateway role, in fact, this is considered a \enquote{Hack where a node-class radio tries to impersonate a gateway}\cite{RpiHatHack}, \doubt{(I'm not sure about this cite (It's a forum))} so this means this hat is designed to be a node-class radio, not a gateway.}
  \item \textit{LoRa Shield for Arduino}\cite{DraginoArdShield}, which is plugged through analog and digital pins.
\end{itemize}

@@

\subsubsubsection{Arduino sketch}
The sketch to take advantage of LoRa Shield is mainly based on the LoRaMAC-in-C library (\cmd{lmic})\footnote{Dragino has a \href{https://github.com/dragino/arduino-lmic}{fork of this library} but has been considered as less accurate than the MCCI version, which is a fork itself from the first port of LMIC library by Matthijs Kooijman.} implemented by \href{https://mcci.com/}{MCCI} whose technical documentation can be found in \cite{MCCI_lmic}

\doubt{}
